Convex Surrogates via Polyhedral Losses

### 2019-02-01 cvx-fin.tex
Adding iteration of thm 29

  We know that $\beta := 1 - \frac{1}{\alpha} \in (0,1)$ as the inequalities are strict.
  Consider two requirements of the polytope: first, for all $i \in \{1,2, \ldots, 6\}, ||v_i|| > 0$.
  Additionally, we know $-\beta < 0$.
  Therefore, there will always be some $S_i$ such that $0 \not \in S_i$.

  By a similar argument to Theorem~\ref{thm:abs-5outcome-not-2embed}, we then must observe $\theta_{j, j+3} > 180^o$ in order to have some $w$ that satisfies our tightness constraint for $j+3$.
  That is, there is an $x \in S_i$ such that $\inprod{v_{j+3}}{x} = 1$.
  However, this implies $\theta_{j+3, j} < 180^o$, and therefore, there is no $x$ such that $\inprod{v_j}{x} = 1$. 
\end{proof}

>>>>

  We know that $\beta := 1 - \frac{1}{\alpha} \in (0,1)$ as the inequalities are strict.
  Consider two requirements of the polytope: first, for all $i \in \{1,2, \ldots, 6\}, ||v_i|| > 0$.
  Additionally, we know $-\beta < 0$.
  Therefore, there will always be some $T_i$ such that $0 \not \in T_i$.
  Specifically, if, as before, we say $||v_1|| \geq ||v_j||$ for all $j \neq 1$, we know that $0 \not \in T_1$.

  By a similar argument to Theorem~\ref{thm:abs-5outcome-not-2embed}, we then must observe $\theta_{j, j+3} > 180^o$ in order to have some $w$ that satisfies our tightness constraint for $j+3$.
  That is, the existence of an $x \in S_i$ such that $\inprod{v_{j+3}}{x} = 1 \implies \theta_{j,j+3} > 180^o$.
  However, this implies $\theta_{j+3, j} < 180^o$, and therefore, there is no $x$ such that $\inprod{v_j}{x} = 1$.

  Like the triangle observed in the previous proof, we observe that $T_1$ is a trapezoid with some constraints that are not tight.
\end{proof}
